Paper Plan\\ FF-Replan: \& RFF\@: Exploiting classical AI planning for uncertain and probabilistic domains

### 2014-03-11 paper-plan/paper-plan.tex
added setup for paper

\section{Motivation}

@@

\subsection{Probabilistic Planning in the Graphplan Framework (1999)~\cite{Blum99probabilisticplanning}}

@@

\subsection{Compiling Conformant Probabilistic Planning Problems into Classical Planning (2013)~\cite{taig2013conformant}}

\section{Conclusion from Related Work and problem statement}

@@

\section{Solution for the problem}

We try to find some solution or direction how to solve the problem

@@

Did it work.

\section{More Literature}

>>>>

%--------------------------------------------------------------------

\section{Introduction}

\begin{itemize}
	\item Introduce planning problem
	\item Introduce planning for uncertainty
	\item Introduce the problem definition and motivation
\end{itemize}

@@

%---------------------------------------------------------------------

\section{Related works}

\begin{itemize}
	\item Introduce the previously read papers
	\item Introduce the current state of the art papers that use deterministic approaches for probablistic domains deadling with uncertainty
\end{itemize}

\subsubsection{Probabilistic Planning in the Graphplan Framework (1999)~\cite{Blum99probabilisticplanning}}

@@

\subsubsection{Compiling Conformant Probabilistic Planning Problems into Classical Planning (2013)~\cite{taig2013conformant}}

%---------------------------------------------------------------------

\subsection{How Much Does a Household Robot Need To Know In Order To Tidy Up? (2013)~\cite{nebel2013much}}

For household robot planning, it appears easy, but actually involves
uncertainty. For tidying things up objects might not be there, or sensing
operations might tell things wrong. This paper looks into conditions for
classical planning in a replanning loop in order to solve nondeterministic
partially observable open domains This paper looks into conditions for
classical planning in a replanning loop in order to solve nondeterministic
partially observable open domains.

\section{Problem formulation}
\begin{itemize}
	\item Summarize shortcomings of the previous solutions
	\item Describe the planning problem
	\item Argument the choice for 2 current papers to analyze
	\item Define how we would like to test the planning algorithms in a domain by our choice
\end{itemize}

@@

%---------------------------------------------------------------------

\section{Domain description}

\begin{itemize}
	\item Describe domains from IPPC
	\item Explain shortcomings
	\item Evaluate a valuable real-world domain in which we can test 2 papers
\end{itemize}

%---------------------------------------------------------------------

\section{Theoretical approach}

\begin{itemize}
	\item Describe how we are using the created domain
	\item show pseudo code for the 2 papers
	\item Introduce the improvements (or combination) of the approaches of the papers fitted for the domain
\end{itemize}

%---------------------------------------------------------------------

\section{Empirical evalution}

\begin{itemize}
	\item Show results for the experiment
	\item Critically analyze the results
	\item Compare with results from the original papers
\end{itemize}

%---------------------------------------------------------------------

@@

\begin{itemize}
	\item Conclude on the succes of the 2 approaches
	\item Conclude the work done in the paper
	\item Hint to some future work developments
\end{itemize}
